% Hacklab operating procedures
\documentclass{article}
\usepackage{palatino}
\usepackage[rightbars,color]{changebar}
\cbcolor{red}
\usepackage{draftwatermark}
\title{Operating Procedures of the Edinburgh Hacklab}
\date{12th March 2011}
\renewcommand{\labelenumi}{Article \arabic{enumi}:}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}}
\begin{document}
\maketitle
\begin{enumerate}
\item Membership
  \begin{enumerate}
  \item Monthly subscription for the Hacklab shall be \pounds 30
    (thirty pounds) per calendar month.
  \item Candidates for membership shall be nominated to the mailing
    list by an existing member.
  \item Existing members have one week to discuss and vote on
    acceptance of the candidate for full membership. The last voting
    email from each member in that week is the only one that will be
    counted.
  \item If at the end of the week, two members vote against the
    candidate, the candidate shall be rejected, otherwise an invite to
    join will be extended by the proposer to the candidate.
  \item The new member shall be given a set of keys upon payment of
    the full amount of the first monthly subscription.
  \end{enumerate} % Membership
\item Agenda and running of the Annual General Meeting
  \begin{enumerate}
  \item At the beginning of the AGM, a chair shall be elected by show
    of hands. It is suggested but not necessary that this be someone
    other than a committee member. The chair shall take minutes and
    post them to the mailing list and wiki after the meeting.
  \item The treasurer shall deliver his or her annual report.
  \item The chair shall then open up the floor to discussion on the
    report and the preceding year in general.
  \item The existing committee shall step down and a new one elected
    using the process defined below.
  \item The members present will discuss and agree the membership
    subscription for the coming year.
  \item The chair will then adjourn the meeting.
  \end{enumerate}
\item Election of Committee
  \begin{enumerate}
  \item The chair shall seek nominations from the floor for the
    position of treasurer.
  \item Once all nominees are in, the chair shall conduct a secret
    ballot of members present for the position of treasurer and the
    winner announced. The election shall be held by Exhaustive Ballot.
  \item The chair shall then seek nominations for the vacant committee
    member positions.
  \item \cbstart Elections for the committee members shall be by Single
    Transferable Vote.\cbend
  \item If the chair wishes to stand for a committee position, another
    chair must be selected by show of hands before the ballot proceeds.
  \item In the event of a tie, the best of three rounds of
    rock/paper/scissors decides the position.
  \end{enumerate}
\item Use of resources
  \begin{enumerate}
  \item Anything labelled not to be touched, is not to be
    touched. Stuff in a labelled box counts as labelled.
  \item Anything unlabelled is OK to be touched and used, but not
    consumed or destroyed. If you break it, you pay for it or replace
    it.
  \item Anything labelled as permissable to consume or destroy, is
    permitted to be consumed or destroyed. If there are terms of use
    on the labelling, observe and respect them.
  \end{enumerate}
\item Amendment
  \begin{enumerate}
  \item These Operating Procedures may be amended by the consensus of
    the membership.
  \end{enumerate} % Organisation
  
\end{enumerate}
\bigskip
\begin{changebar}
Date drafted: 12th March 2011
\end{changebar}
\end{document}
